### 2024-09-10 Article/main.tex
Some adjustments

\begin{example}
    An equalizer in $\mathbf{EgGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$. The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
\end{example}

The two previous examples shows that the category $\mathbf{EgGrph}$ has both equalizer and finite products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EgGrph}$ has finite limits.

\begin{example}
    Given two parallel morphisms $f, g: \mathcal{G \rightarrow H}$ in $\mathbf{EgGrph}$, the coequalizer $(\mathcal{C}, c)$ is the graph 
\end{example}

>>>>

\begin{example}
    An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$. The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
\end{example}

The two previous examples shows that the category $\mathbf{EqGrph}$ has both equalizer and finite products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits.
